---
title: "How many people use my R packages"
author: "Alessio Crippa"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, comment = "")
options(width = 110)
library(tidyverse)
library(lubridate)
library(plotly)
library(scales)
library(DT)
library(googleVis)
library(shiny)
library(shinyjs)

dwnld <- read.table("pkgs_dwnld.txt", stringsAsFactors = FALSE) %>%
  mutate(
    date = as.Date(date),
    month = floor_date(date, "month"),
    week = floor_date(date, "week")
  ) %>%
  as_tibble()
```

------------

The aim of this interactive R markdonw is to dispaly the number of downloads of the R packages that I developed, i.e. the `dosresmeta` and `hetmeta` packages, both available on CRAN ([`dosresmeta`](https://cran.r-project.org/package=dosresmeta), [`hetmeta`](https://cran.r-project.org/package=hetmeta)) and GitHub ([`dosresmeta`](https://github.com/alecri/dosresmeta), [`hetmeta`](https://github.com/alecri/hetmeta)). 
The `alecri` R package is an (incomplete) collection of functions and data usefull in my day-life work, but it's not considered in this document. More material and working example can be found at https://alecri.github.io/software/ .

The data about the number of downloads come from CRAN log files of the RStudio cloud CRAN. Read the  [blog post](https://blog.rstudio.com/2013/06/10/rstudio-cran-mirror/) by Hadley Wickham for more details.

<br/>

**Document last updated**:  `r Sys.Date()`

**Data last updated**: `r max(dwnld$date)`

-----


## Description of the available data

The data files (i.e. log files) from the (Rstudio CRAN mirror)[https://cran.rstudio.com/] have been downloaded and read in R using the `installr` package. 
Each log file had the following variables:

- date
- time (in UTC)  
- size (in bytes)  
- r_version, version of R used to download package  
- r_arch (i386 = 32 bit, x86_64 = 64 bit)  
- r_os (darwin9.8.0 = mac, mingw32 = windows)  
- package  
- country, two letter ISO country code. Geocoded from IP using MaxMind's free database  
- ip_id, a daily unique id assigned to each IP address.  

This is a snapshot of the available information.

```{r}
glimpse(dwnld)
```

```{r data}
dwnld_sub <- reactive({
  dwnld_sub <- dwnld
  #date_range <- floor_date(input$date_range, input$time_unit)
  if (!all(range(dwnld$date) == input$date_range)){
    # dwnld_sub <- filter(dwnld_sub, UQ(as.name(input$time_unit)) >= date_range[1],
    #                     UQ(as.name(input$time_unit)) <= date_range[2])
    dwnld_sub <- filter(dwnld_sub, date >= min(input$date_range),
                        date <= max(input$date_range))
  }
  if (input$pkgs != "all")
  dwnld_sub <- filter(dwnld_sub, package == input$pkgs)
  dwnld_sub
})

dwnld_count <- reactive({
  dwnld_sub() %>%
  group_by_("package", input$time_unit) %>%
  count()
})

dwnld_map <- reactive({
  dwnld_sub() %>%
    group_by(country, package) %>%
    count()
})
dwnld_map_all <- reactive({
  dwnld_map() %>%
    group_by(country) %>%
    summarise(n = sum(n)) %>%
    arrange(desc(n))
})
dwnld_map_dosresmeta <- reactive({
  dwnld_map() %>%
    filter(package == "dosresmeta") %>%
    arrange(desc(n))
})
dwnld_map_hetmeta <- reactive({
  dwnld_map() %>%
    filter(package == "hetmeta") %>%
    arrange(desc(n))
})

```

----

<h2>Total number of downloads per `r renderText(input$time_unit)`</h2>

Here you can find the total number of downloads grouped by month or week. 

```{r tot_dwnld_table}
inputPanel(
  id = "form",
  selectInput("time_unit", label = "Display total number of downloads per:",
            choices = c("month", "week"), selected = "month"),
  radioButtons("pkgs", "Select the desired package", 
             c("all", "dosresmeta", "hetmeta"), "all"),
  dateRangeInput("date_range", label = "Date range",
               start = min(dwnld$date), end = max(dwnld$date),
               min = min(dwnld$date), max = max(dwnld$date)),
  actionButton("resetAll", "Reset all")
)
useShinyjs(rmd = TRUE)
observeEvent(input$resetAll, reset("form"))
```

```{r}
renderDataTable({
  dwnld_count()
})
```

</br></br>

Below the time serie with the total number of downloads per month or week for the selected packages.


```{r tot_dwnld_ts, echo=FALSE}
output$trend <- renderPlotly({
  p_trend <- ggplot(dwnld_count(), aes_string(input$time_unit, "n", col = "package")) + 
    geom_line() + 
    theme_light() + theme(panel.border = element_blank(), axis.line = element_line()) +
    labs(y = paste("Total number of downloads per", input$time_unit, "\n"))
  if (input$log)
    p_trend <- p_trend + scale_y_continuous(trans = "log",
                             breaks = trans_breaks("log", function(x) round(exp(x))))
  ggplotly(p_trend)
})
plotlyOutput("trend")
checkboxInput("log", "Dispaly counts on a log-scale", FALSE)
```

<br/>

-----------------

## Downloads by country


```{r maps}
output$map_dosresmeta <- renderGvis({
  if (input$pkgs == "hetmeta") return(NULL)
  geo <- gvisGeoChart(dwnld_map_dosresmeta(), locationvar = 'country', colorvar = 'n',
                    options = list(height = 400, width = 600, colors = "green"))
  tbl <- gvisTable(dwnld_map_dosresmeta(), options = list(height = 400, width = 300))
  gvisMerge(geo, tbl, horizontal = TRUE, tableOptions = "cellspacing=50")
})
output$map_hetmeta <- renderGvis({
  if (input$pkgs == "dosresmeta") return(NULL)
  geo <- gvisGeoChart(dwnld_map_hetmeta(), locationvar = 'country', colorvar = 'n',
                    options = list(height = 400, width = 600, colors = "red"))
  tbl <- gvisTable(dwnld_map_hetmeta(), options = list(height = 400, width = 300))
  gvisMerge(geo, tbl, horizontal = TRUE, tableOptions = "cellspacing=50")
})
output$map_all <- renderGvis({
  if (input$pkgs != "all") return(NULL)
  geo <- gvisGeoChart(dwnld_map_all(), locationvar = 'country', colorvar = 'n',
                    options = list(height = 400, width = 600, colors = "purple"))
  tbl <- gvisTable(dwnld_map_all(), options = list(height = 400, width = 300))
  gvisMerge(geo, tbl, horizontal = TRUE, tableOptions = "cellspacing=50")
})
```

```{r}
tabsetPanel(
  tabPanel("dosresmeta", htmlOutput("map_dosresmeta")), 
  tabPanel("hetmeta", htmlOutput("map_hetmeta")),
  tabPanel("all", htmlOutput("map_all"))
)
```

<br/><br/>

-----------------

## Descriptives

<br/>

**Total number of downloads**
```{r}
renderTable(
dwnld_sub() %>%
  group_by(package) %>%
  count()
)
```

**Different versions with range dates**
```{r}
renderTable(
dwnld_sub() %>%
  group_by(package, version) %>%
  summarize(n = n(),
            min_date = as.character(min(date)),
            max_date = as.character(max(date)))
)
```

