---
title: "dosresmeta usage"
author: "Alessio Crippa"
date: "September 24, 2015"
output:
  html_document:
    self_contained: no
runtime: shiny
---


The `dosresmeta` package was first released on the 11st September 2011 to perform dose-response meta-analysis in R. Detailed documentation can be found [here](https://cran.r-project.org/web/packages/dosresmeta/dosresmeta.pdf).  
The following report is based on the downloads of `dosresmeta` from the log files of the [RStudio cloud CRAN](http://cran-logs.rstudio.com/) and is update to the 12nd April 2016.  
The interactive R Markdown document wase generated using Shiny; to learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

By checking the following check box the analyses are restricted to the downloads from unique ip addresses for every version of the package.
```{r, echo=FALSE}
checkboxInput("ip", label = "unique IP", value = FALSE)
```


--------------------------------------------------------------------------------

```{r, echo=FALSE, include=FALSE}
## Pkg required
require("plyr")
require("sp")
require("shiny")
require("installr")
require("ggplot2")
require("googleVis")
require("scales")                      ## for date format
require("plotly")
#op <- options(gvis.plot.tag='chart')   ## for googleVis
Sys.setenv("plotly_username"="alecri")
Sys.setenv("plotly_api_key"="nr287vef19")

## Read data
#data_tot <- read.table("C://Users/alecri/Dropbox/KI/Packages/usageDosresmeta/dosresmeta_download.txt", stringsAsFactors = F)
#data_tot <- read.table("/Users//alecri/Dropbox/KI/Packages/usageDosresmeta/dosresmeta_download.txt", stringsAsFactors = F)
data_tot <- read.table("dosresmeta_download.txt", stringsAsFactors = F)
data_tot$date <- as.Date(data_tot$date)
data_tot$month <- as.Date(cut(data_tot$date, breaks = "month"))
data_tot$week <- as.Date(cut(data_tot$date, breaks = "week",
                            start.on.monday = FALSE))

dataAct <- reactive({
  data <- if (input$ip == TRUE){
   data_tot[!duplicated(data_tot[c("ip_id", "version")]), ]
  } else {
     data_tot
  }
  data
})

```


## Number of downloads of *dosresmeta* package

From the 11/10/2011 to the 12/04/2016 (`r renderText(length(unique(dataAct()$date)))` days) the `dosremeta` package has been downloaded `r renderText(nrow(dataAct()))` times

```{r, echo=FALSE}
renderTable({
   tabVersion <- t(cbind.data.frame(table(dataAct()$version)))
   colnames(tabVersion) <- paste("Version", tabVersion[1, ])
   rownames(tabVersion)[2] <- "downloads"
   data.frame(tabVersion[2, , drop = FALSE])
  })
```

--------------------------------------------------------------------------------

```{r, echo=FALSE, results='asis'}
inputPanel(
   selectInput("by", label = h3("by:"), 
                         choices = list("day" = "date", "week" = "week",
                                        "month" = "month"), selected = "week"),
   radioButtons("type", label = h3("type:"),
                          choices = list("Bar chart" = "bar", "Line chart" = "line"), selected = "bar")
)


## Summing downloads for weeks and months
dataDwn <- reactive({
  if (input$by == "date"){
     counts <- ddply(dataAct(), .(date), summarize, quantity = length(date))
  }
  if (input$by == "week"){
     counts <- ddply(dataAct(), .(week), summarize, quantity = length(week))
  }
   if (input$by == "month"){
      counts <- ddply(dataAct(), .(month), summarize, quantity = length(month))
   }
   counts
})

output$trend <- renderPlotly({
   p <- ggplot(data = dataDwn(), aes_string(input$by, "quantity")) +
      scale_x_date(labels = date_format("%Y-%m-%d")) +
      stat_summary(fun.y = identity, geom = input$type)
   ggplotly(p)
})
#plotlyOutput("trend")
plotlyOutput("trend")
```

--------------------------------------------------------------------------------

## World Wide downloads

<!--
```{r, echo=FALSE, include=FALSE}
data <- data_tot[!duplicated(data_tot$ip_id), ]
counts <- cbind.data.frame(table(data$country))
names(counts) <- c("country", "count")
data("WorldBordersData", envir = environment(), package = "installr")
ISO_full <- get("ISO_full")
colcode <- numeric(length(ISO_full))
names(colcode) <- ISO_full
dnl_places <- names(colcode[which(names(colcode) %in% as.character(counts$country))])
rownames(counts) <- counts$country
colcode[dnl_places] <- counts[dnl_places, "count"]
world@data$id <- rownames(world@data)
world.points <- fortify(world, by = "id")
names(colcode) <- rownames(world@data)
world.points$dnls <- colcode[world.points$id]
world.map <- ggplot(data = world.points) + 
  geom_polygon(aes_string(x = "long", y = "lat", group = "group", fill = "dnls"), color = "black") +
  coord_equal() + scale_fill_gradientn(colours = c("white", "yellow", "red"), 
                                       name = "Downloads", values = c(0, 0.25, 1)) + 
  labs(title = paste("downloads from the Rstudio '0-Cloud' CRAN mirror by country\nfrom ",
                     min(data$date), " to ", max(data$date), "\n(Total downloads: ",
                     sum(counts$count), ")", sep = ""))
world.map
```
-->

```{r, results = 'asis', echo=FALSE}
dataTab <- reactive({
  counts <- cbind.data.frame(table(dataAct()$country))
  names(counts) <- c("country", "count")
  counts <- counts[order(counts$count, decreasing = TRUE, na.last = TRUE), ]
  counts
})

output$map <- renderGvis({
   geo <- gvisGeoChart(dataTab(), locationvar = 'country', colorvar = 'count',
                    options = list(height = 400, width = 650))
   tbl <- gvisTable(dataTab(), options = list(height = 400, width = 200))
   gvisMerge(geo, tbl, horizontal = TRUE, tableOptions = "cellspacing=50")
})
htmlOutput("map")
```





In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



